### 2017-01-13 doc/manuscript.Rmd
First (rough) draft of discussion - general findings

We found that in a Canadian population of mainly female and European ancestry, 
the specific TAGFA composition was strongly associated with insulin sensitivity
and moderately associated with beta-cell function. In particular, TAGFA myristic 
acid (14:0), 7-tetradecenoic acid {{ confirm }} (14:1n-7), palmitic acid (16:0),
and palmitoleic acid (16:1n-7) all strongly and negatively predicted lower
insulin sensitivity. While

Interpretation:

@@

>>>>

## Overall conclusion

We found that in an at-risk for diabetes Canadian population of mainly female
and European ancestry, the specific TAGFA composition was strongly associated
with insulin sensitivity and moderately associated with beta-cell function. In
particular, TAGFA myristic acid (14:0), 7-tetradecenoic acid {{ confirm }}
(14:1n-7), palmitic acid (16:0), and palmitoleic acid (16:1n-7) all strongly and
negatively predicted lower insulin sensitivity. {{confirm}} While most TAGFA
were not associated with beta-cell function, {{confirm after checking models}}
two fatty acids, 16:0 and 18:1n-7, were associated negatively and positively,
respectively, with both measures of beta-cell function. We also found that four
TAGFA (14:0, 14:1n-7, 16:0, 16:1n-7) clustered together, and that also strongly 
predicted lower insulin sensitivity. These four fatty acids are also involved in
the DNL of refined and simple carbohydrates {{cite}}. Our results, which are in
agreement with the current literature, suggest that higher intakes of simple
carbohydrates or higher activity of DNL may increase the risk for diabetes,
likely through worsening insulin sensitivity.

@@

## Interpretation and previous literature
